Association between trauma severity models and opportunities for improvement:

### 2022-10-18 manuscript.Rmd
made a table

Outcome data
------------

<!-- Cohort study — Report numbers of outcome events or summary measures
over time -->

@@

The odds ratio for TRISS was `r t.stats[['or']]` (95% CI: `r t.stats[['or.ci']]`, p-value: `r t.stats[['or.p']]`). When plotting the ROC, the AUC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The integrated calibration index for TRISS was `r t.stats[['ici']]`.

The odds ratio for NORMIT was `r n.stats[['or']]` (95% CI: `r n.stats[['or.ci']]`, p-value: `r n.stats[['or.p']]`). When plotting the ROC, the AUC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`). The integrated calibration index for NORMIT was `r n.stats[['ici']]`.

`r t.plot.roc`
`r t.plot.acc`

`r n.plot.roc`
`r n.plot.acc`

>>>>

Detailed totals for missing data for each required parameter are given in table 2. The total number of missing parameters is greater than the number of participants excluded for missing parameters. This is because some patients lacked multiple required parameters.

```{r gt table, echo = FALSE}
missing
```

@@

The odds ratio for TRISS was `r t.or['or']` (95% CI: `r t.or[2]`-`r t.or[3]`, p-value: `r t.stats[['or.p']]`). The ROC is plotted in Figure 3. The AUC for the ROC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The integrated calibration index for TRISS was `r t.stats[['ici']]`. The accuracy curve is shown in Figure 4. The best accuracy was `r t.stats[['acc.nrs']][1]` and was found at the cutoff `r t.stats[['acc.nrs']][2]`.

```{r, echo = FALSE}
plot(t.stats[['perf']], main="Fig 3. TRISS Receiver Operating Characteristic Curve.", colorize = TRUE)
```

```{r, echo = FALSE}
t.plot.acc <- plot(t.stats[['acc']], main="Fig 4. TRISS Accuracy Curve.")
```

The odds ratio for NORMIT was `r n.or['or']` (95% CI: `r n.or[2]`-`r n.or[3]`, p-value: `r n.stats[['or.p']]`). The ROC is plotted in Figure 5. The AUC for the ROC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`). The integrated calibration index for NORMIT was `r n.stats[['ici']]`. The accuracy curve for NORMIT is shown in Figure 5. The best accuracy was `r n.stats[['acc.nrs']][1]` and was found at the cutoff `r n.stats[['acc.nrs']][2]`.

```{r, echo = FALSE}
plot(n.stats[['perf']], main="Fig 5. NORMIT Receiver Operating Characteristic Curve.", colorize = TRUE)
```

```{r, echo = FALSE}
n.plot.acc <- plot(n.stats[['acc']], main="Fig 6. NORMIT Accuracy Curve.")
```
